---
output: 
  html_document:
    self_contained: no
---
#Omen:

###Imported file:
```{r  echo=FALSE, message=FALSE, warning=FALSE}
library(pander)
    inputcsv<-upx()

 s = c("January","February","March","April","May","June","July","August","September","October","November","December")

inp<-upx()
colnames(inp)<-c("date","val")
tab<-matrix(inp$val, ncol=12, nrow=length(inp$val)/12)
tab<-as.data.frame(tab)
colnames(tab)<-s
panderOptions("digits", 2)
pander(tab)
```
###Statistics:
```{r echo=FALSE, warning=FALSE, message=FALSE}
    FirstYear<-as.numeric(substr(as.character(dateinput()[2]),1,4))
    FirstMonth<-as.numeric(substr(as.character(dateinput()[2]),6,7))
    FirstForecast <-100*FirstYear+FirstMonth #Get first forecast
    insample <- ts(upx()$QTY[upx()$Date<FirstForecast],frequency=fileppy())
    
```
**Mean:** `r round(mean(insample, na.rm=T),2) `  
**Median:** `r round(median(insample, na.rm=T),2)`  
**Standard Deviation:** `r round(sd(insample, na.rm=T),2)`  
**Coefficient of Variation:** `r paste0(round(((sd(insample, na.rm=T)/mean(insample, na.rm=T))*100),2),"%") `  
**Variance:** `r  round(var(insample, na.rm=T),2)`  
**Linear Correlation Coefficient:** `r round(cor(1:length(insample),insample),2)`  
**ACF Plot**
```{r statplot, echo=FALSE, warning=FALSE, message=FALSE}
    library("ggplot2")
    datacf<-as.data.frame(acf(insample, plot=F,na.action=na.pass)$acf)
    colnames(datacf)<-"acf"
    datacf$Observations<-as.numeric(row.names(datacf))
    datacf<-datacf[-c(1), ]
    ggplot(data=datacf, aes(x=Observations,y=acf, fill=acf))+ geom_bar(stat="identity") +scale_fill_gradient(low="#b6daed",high="#00527f")+ theme_bw() +
    theme(legend.position="bottom")
```


 **PACF Plot**  
```{r statplotb, echo=FALSE, warning=FALSE, message=FALSE}
     library("ggplot2")
    datapacf<-as.data.frame(pacf(insample, plot=F,na.action=na.pass)$acf)
    colnames(datapacf)<-"pacf"
    datapacf$Observations<-as.numeric(row.names(datapacf))
    datapacf<-datapacf[-c(1), ]
    ggplot(data=datapacf, aes(x=Observations,y=pacf, fill=pacf))+ geom_bar(stat="identity") +scale_fill_gradient(low="#b6daed",high="#00527f")+theme_bw() +
    theme(legend.position="bottom")
```


###Outliers
```{r outblock, echo=FALSE, warning=FALSE, message=FALSE}

    datatable<-OutliersTable1()[,c("Original Timeseries","Adjusted Timeseries")]

```


```{r outplot, echo=FALSE, warning=FALSE, message=FALSE}
    library("ggplot2")
data2<-datatable
data2$index=1:nrow(datatable)
 datamelt<-melt(data2, id="index")
    ggplot(data=datamelt, aes(x=index, y=value, colour=variable))+geom_line()+ theme_bw()+scale_colour_brewer(palette="YlGnBu") +
    theme(legend.position="bottom")


```


###Decompose
```{r decompos, echo=FALSE, warning=FALSE, message=FALSE}

    seasondata<-Decomposition()
    seasondata<-seasondata[,c('Randomness',"Cyrcle","Trend","Seasonality")]
    seasondata$Index<-as.numeric(row.names(seasondata))
   # seasondata<-melt(seasondata, id="Index")
    Randomness<- ggplot(data=seasondata, aes(x=Index, y=Randomness))+geom_line()+ theme_bw() +
    theme(legend.position="bottom")
    Cyrcle<-ggplot(data=seasondata, aes(x=Index, y=Cyrcle))+geom_line()+ theme_bw() +
    theme(legend.position="bottom")
    Trend<- ggplot(data=seasondata, aes(x=Index, y=Trend))+geom_line()+ theme_bw() +
    theme(legend.position="bottom")
    Seasonality<- ggplot(data=seasondata, aes(x=Index, y=Seasonality))+geom_line()+ theme_bw() +
    theme(legend.position="bottom")
    # 
    
        data<-Decomposition()$LE
    if (input$removeoutliersdec==F){
      indata<-upx()
      indata[is.na(indata)] <- 0 
      FirstYear<-as.numeric(substr(as.character(dateinput()[2]),1,4))
      FirstMonth<-as.numeric(substr(as.character(dateinput()[2]),6,7))
      FirstForecast <-100*FirstYear+FirstMonth #Get first forecast
      InSample <- ts(indata$QTY[indata$Date<FirstForecast])
      InSample[is.na(InSample)] <- 0
    }else{
      InSample<-(OutliersTable1()[,c("Adjusted Timeseries")])
    }
    
    ppy=input$decfr
    if (ppy=='Unknown')
      ppy = findppy(InSample)
    ppy<-as.numeric(ppy)
    max <- ppy
    
    x <- seq_along(data)
    dataLE <- split(data, ceiling(x/max))
    dataLE <- as.data.frame(dataLE)
    dataLE$Observations<-as.numeric(row.names(dataLE))
    simsubmelt = melt(dataLE,id="Observations")
    Seasonplot<- ggplot(data=simsubmelt, aes(x=Observations, y=value, colour=variable))+geom_line()+ theme_bw() +
    theme(legend.position="bottom")

```
#####Randomness
```{r rand, echo=FALSE, warning=FALSE, message=FALSE}
Randomness
```

#####Cycle
```{r cyr, echo=FALSE, warning=FALSE, message=FALSE}
Cyrcle
```

#####Trend
```{r tren, echo=FALSE, warning=FALSE, message=FALSE}
Trend
```

#####Seasonality
```{r seasss, echo=FALSE, warning=FALSE, message=FALSE}
Seasonality
```

#####Seasonplot
```{r trf, echo=FALSE, warning=FALSE, message=FALSE}
Seasonplot
```

###Smoothing

#####Chosen Smoothing Method: `r input$smoothmethodin `  
```{r echo=FALSE, warning=FALSE, message=FALSE}
    dataaa<-as.data.frame(smbplot())
   # dataaa$original<-insample
    dataaa$Observations<-as.numeric(row.names(dataaa))
   # colnames(dataaa)<-c("Smooth","Original","Observations")
    smoothmelt<- melt(dataaa,id="Observations")
    ggplot(data=smoothmelt, aes(x=Observations, y=value, colour=variable))+geom_line()+scale_colour_brewer(palette="Set1") + theme_bw() +
    theme(legend.position="bottom")
```

###Temporal Aggregation
```{r echo=FALSE, warning=FALSE, message=FALSE}
    data<-taggdata()
data$Observations<-1:nrow(data)
    simsubmelt = melt(data,id="Observations")
    ggplot( data = simsubmelt, aes(x=Observations, y = value, colour = variable))+geom_line()+scale_colour_brewer(palette="YlGnBu") + theme_bw() +
    theme(legend.position="bottom")

```

###Forecasts

```{r echo=FALSE, warning=FALSE, message=FALSE}

    datatable<-FinalTable()
    colnames(datatable)[colnames(datatable)=="Date"] <- "TimeStamp"
    colnames(datatable)[colnames(datatable)=="qvalue"] <- "Value"
    colnames(datatable)[colnames(datatable)=="qvaluec"] <- "Value Deseasonalized"
    colnames(datatable)[colnames(datatable)=="fqvalueb"] <- "Value Forecast"
    simsub=datatable
    
    
    
    # #Add Confidence Levels
     if (input$clin!="none"){
       TSSY<-as.numeric(substr(as.character(dateinput()[2]),1,4))
       TSSM<- as.numeric(substr(as.character(dateinput()[2]),6,7))
       qtycl1a<-ts(forecastQTYe()$CL1,frequency=fileppy(),start = c(as.numeric(TSSY),as.numeric(TSSM)))
       qtycl1.m<- data.frame(yr=round(time(qtycl1a), digits = 2),qtycl1=as.matrix(qtycl1a))
       datatable<-merge(datatable,qtycl1.m,by = "yr", all=TRUE)
       qtycl2a<-ts(forecastQTYe()$CL2,frequency=fileppy(),start = c(as.numeric(TSSY),as.numeric(TSSM)))
       qtycl2.m<- data.frame(yr=round(time(qtycl2a), digits = 2),qtycl2=as.matrix(qtycl2a))
       datatable<-merge(datatable,qtycl2.m,by = "yr", all=TRUE)
       colnames(datatable)[colnames(datatable)=="qtycl1"] <- "Confidence Level 1"
       colnames(datatable)[colnames(datatable)=="qtycl2"] <- "Confidence Level 2"}
    simsub=datatable
    
     simsub$ID<-1:nrow(simsub)
    preparation<-smbplot()
    if (input$considersmoothing==F) #if smoothing is FALSE ignore last column
      preparation<-preparation[,1:(ncol(preparation)-1)]
    preparation$ID<-1:nrow(preparation)
    simsub<- merge(simsub,preparation, by="ID", all=TRUE)
    if (input$considersmoothing==T){
      level<-chartr("012345678", "ABCDEFGHI", ncol(smbplot()))
      colnames(simsub)[colnames(simsub)=="Value Forecast"] <- paste0(level, ". Value Forecast")
      if (input$clin!="none"){
        level1<-chartr("012345678", "ABCDEFGHI", ncol(smbplot())+1)
        colnames(simsub)[colnames(simsub)=="Confidence Level 1"] <- paste0(level1, ". Confidence Level 1")
        
        level2<-chartr("012345678", "ABCDEFGHI", ncol(smbplot())+2)
        colnames(simsub)[colnames(simsub)=="Confidence Level 2"] <- paste0(level2, ". Confidence Level 2")
        
        simsub<-simsub[,c(c("DatePlot",paste0(level, ". Value Forecast"),paste0(level1, ". Confidence Level 1"),paste0(level2, ". Confidence Level 2")),colnames(smbplot()))]
        
      }else {
        simsub<-simsub[,c(c("DatePlot",paste0(level, ". Value Forecast")),colnames(smbplot()))]
      }
       
    } else {
      level<-chartr("012345678", "ABCDEFGHI", ncol(smbplot())-1)
  
      colnames(simsub)[colnames(simsub)=="Value Forecast"] <- paste0(level, ". Value Forecast")
      
      if (input$clin!="none"){
        level1<-chartr("012345678", "ABCDEFGHI", ncol(smbplot()))
        colnames(simsub)[colnames(simsub)=="Confidence Level 1"] <- paste0(level1, ". Confidence Level 1")
        
        level2<-chartr("012345678", "ABCDEFGHI", ncol(smbplot())+1)
        colnames(simsub)[colnames(simsub)=="Confidence Level 2"] <- paste0(level2, ". Confidence Level 2")
        
        simsub<-simsub[,c(c("DatePlot",paste0(level, ". Value Forecast"),paste0(level1, ". Confidence Level 1"),paste0(level2, ". Confidence Level 2")),colnames(smbplot()[1:(ncol(smbplot())-1)]))]
        
      }else {
        simsub<-simsub[,c(c("DatePlot",paste0(level, ". Value Forecast")),colnames(smbplot()[1:(ncol(smbplot())-1)]))]
      }
      
      
    }
    simsubmelt = melt(simsub,id="DatePlot")
    ggplot(data=simsubmelt, aes(x=DatePlot, y=value, colour=variable))+geom_line()+scale_colour_brewer(palette="Set1") + theme_bw() +
    theme(legend.position="bottom")

```
###Judgemental Adjustments
```{r echo=FALSE, warning=FALSE, message=FALSE}

    jdata<-as.data.frame(judgedata())
    jdata$Point<-1:nrow(jdata)
    jsubmelt = melt(jdata, id="Point")
    ggplot(data=jsubmelt, aes(x=Point, y=value, colour=variable))+geom_line()+scale_colour_brewer(palette="Set1") + theme_bw() +
    theme(legend.position="bottom")


```


###Errors

####Insample-Forecast Model Errors
```{r  echo=FALSE, message=FALSE, warning=FALSE}
library(pander)

panderOptions("digits", 2)
pander(errors())
```
####Out Of Sample-Forecasts Errors
```{r  echo=FALSE, message=FALSE, warning=FALSE}
library(pander)
panderOptions("digits", 2)
pander(forecasterrors())

```
####Errors - Visualization
```{r echo=FALSE, warning=FALSE, message=FALSE}

    scdata<-data.frame(cbind(head(FinalTable()$fqvalue, length(insample)),head(FinalTable()$qvalue, length(insample))))

    colnames(scdata)<-c("Forecast Model","Insample")
    scdata$insample2<-scdata$Insample
    scdatamelt<-melt(scdata,id="Insample")
    ggplot(scdatamelt, aes(x=Insample, y=value, color=variable)) + geom_point(shape=18)+scale_colour_brewer(palette="Set1")

    error1<-ErrorsCalculation(head(FinalTable()$fqvalue, length(insample)), head(FinalTable()$qvalue, length(insample)))
    errorqty<-t(error1[[1]])
    colnames(errorqty)<-c("e","pe","ape","se","sape")
    scdata<-data.frame(rn=1:length(errorqty[,c("e")]))
    scdata$error<-errorqty[,c("e")]
    ggplot(scdata, aes(x=rn, y=error, color=error)) + geom_bar(stat="identity") +
    theme(legend.position="bottom")
    
    FirstYear<-as.numeric(substr(as.character(dateinput()[2]),1,4))
    FirstMonth<-as.numeric(substr(as.character(dateinput()[2]),6,7))
    FirstForecast <-100*FirstYear+FirstMonth #Get first forecast
    
    insample <- ts(upx()$QTY[upx()$Date<=FirstForecast],frequency=1) 
    allsample<-ts(upx()$QTY,frequency=1)
    lengthdfa<-length(allsample)-length(insample)
    if (lengthdfa>0){
    if (length(insample)<length(upx()$QTY)) {
      dfa<-tail(upx()$QTY,as.numeric(lengthdfa))
    }else{
      dfa<-NULL
    }
    dfb<-finalforecasts()#tail(na.omit(FinalTable()[,c("fqvalue")]),input$horizonin)
    if (length(na.omit(dfa))>=length(na.omit(dfb))) {
      yd<-as.numeric(input$horizonin)

    } else{
      yd<-length(dfa)

    }
    df1<-as.data.frame(head(dfa,yd))
    df2<-as.data.frame(head(dfb,yd))

    df1$rn<-1:yd
    df2$rn<-1:yd

    scdata<-merge(df1,df2,by="rn",all.y=TRUE)
    # scdata<-na.omit(scdata)
    colnames(scdata)<-c("rn","Out Of Sample","Forecasts")
    scdata<-scdata[,c("Out Of Sample","Forecasts")]
    scdata$OutOfSample<-scdata[,c("Out Of Sample")]
    scdatamelt<-melt(scdata,id="OutOfSample")
    ggplot(scdatamelt, aes(x=OutOfSample, y=value, color=variable)) + geom_point(shape=18)+scale_colour_brewer(palette="Set1")


     insample <- ts(upx()$QTY[upx()$Date<=FirstForecast],frequency=1)
    allsample<-ts(upx()$QTY,frequency=1)
    lengthdfa<-length(allsample)-length(insample)
    if (length(insample)<length(upx()$QTY)) {
      dfa<-tail(upx()$QTY,as.numeric(lengthdfa))
    }else{
      dfa<-NULL
    }
    dfb<-finalforecasts()#tail(na.omit(FinalTable()[,c("fqvalue")]),input$horizonin)
    if (length(na.omit(dfa))>=length(na.omit(dfb))) {
      yd<-as.numeric(input$horizonin)

    } else{
      yd<-length(dfa)

    }
    df1<-head(dfa,yd)
    df2<-head(dfb,yd)

    errorqty1a<-ErrorsCalculation(df1, df2)

    errorqty<-t(errorqty1a[[1]])
    colnames(errorqty)<-c("e","pe","ape","se","sape")
    scdata<-data.frame(rn=1:length(errorqty[,c("e")]))
    scdata$error<-errorqty[,c("e")]
    scdata$zero<-0
    ggplot(scdata, aes(x=rn, y=error, color=error)) + geom_bar(stat="identity") +
    theme(legend.position="bottom")
    texto<-" "

    }else{
     texto<-"The imported time-series has no out-of-sample data to compare with the forecasts."
     texto
   }
    
```
`r print(texto)` 

